Framing Effects in the Wild

### 2022-09-07 paper/Manuscript_Framing.Rmd
update
FIx figure placement,
improve case description, empirical strategy, results

---
title: "Framing Effects in the Wild"
author: "Nicolai Berk"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: false
    fig_caption: yes
    includes:
      in_header: preamble.tex
# subtitle: Manuscript prepared for the 12th Annual Conference of the European Political Science Association in Prague, Czech Republic
fontsize: 12pt
geometry: margin=1.5in
abstract: "Does news framing affect public opinion? While a large body of experimental work suggests that individual attitudes can be easily altered by emphasizing different aspects of an issue, little is known about how these studies translate into the real world. I exploit a rare change in the migration framing of the major German tabloid *Bild* to study whether experimental estimates of framing effects translate into the real world. In a first step, I develop a framework for the measurement of emphasis frames in political communication using supervised machine learning. Using this framework, I show that the emphasis of crime in *Bild*'s migration coverage severely increased. Second, I employ a difference-in-differences design using panel data from over 16,000 individuals in ten waves to assess the precise impact of this shift on migration attitudes. The findings show that, despite a major change in migration framing, a clear null effect on immigration attitudes and related variables can be observed. Tracing three key assumptions underlying the translation of experimental effect estimates suggests that news framing affects attitudes only within limited windows of opportunity early in the politicization of political issues."
bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
nocite: |
  @CologneReport2016
---

@@

knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center', eval = T)

@@

***Association hypothesis*****: When an individual is exposed more to a specific consideration about an issue, their association of the issue with this consideration should be strengthened.**

***Evaluation hypothesis*****: When an individual is exposed more to a specific positive/negative consideration about an issue, their attitude about the overall issue should become more positive/negative.**

@@

In order to test whether changing news content affected political attitudes, I exploit an editorial change in the largest German newspaper, *Bild*. As I will show, this editorial change resulted in a substantial shift in the papers' migration framing and is hence ideal to assess the effect of within-newspaper content shifts. The fielding of a large-scale panel survey in the same period allows to assess the precise impact of this change in news content on consumers' migration attitudes.

@@

In the summer of 2015, Germany became sanctuary for around 800,000 refugees who had fled war, violence, and famine in Syria and elsewhere. The German public debated how to deal with the newly arriving and for the first time since the post-war years, a radical right party was likely to win representation in the national parliament. Surprisingly, given its traditional populist style and right-wing takes on migration, the major tabloid newspaper *Bild* initially maintained a somewhat balanced coverage of the newly arriving, which - although portraying migrants more negatively than other outlets - even started a campaign called "#RefugeesWelcome" to gather support for the newly arriving [@Maurer2019; see @BildRefugeesWelcome]. This was often connected to chief editor Kai Diekmann, who hosted a refugee family in his home [@BR2015Diekmann].

In December 2016, Axel Springer, the company owning Bild, announced that Diekmann will leave the company. Less than a week after, it became public that prosecutors investigate Diekmann for sexual harassment. While the company claimed that this was not the reason for Diekmann's departure, the process might have been sped up as a result of the investigations\footnote{According to a former editor of the newspaper I talked to, rumors in the company at the time support this interpretation of events.} [@Spiegel2017Diekmann]. The migration coverage in *Bild* severely changed when Diekmann left the newspaper in February 2017 and Julian Reichelt took over the position as editor-in-chief. The paper increasingly started painting a picture of refugees as criminals on the tabloid's front page [@Niggemeyer2018Bild; @DLF2018Reichelt]. Headlines like "I killed 40 people and want asylum" increasingly dominated the migration coverage of the newspaper. In a speech months before he took over the position as chief editor, Reichelt outlined his motivation for such a shift in migration coverage: "I can assure you: nothing has hurt [*Bild*] economically as much as our clear, humane, empathetic stance in the refugee crisis" \footnote{Reichelt in a speech at Deutschlandfunk's conference "Formate des Politischen 2016": \url{https://vimeo.com/190347766}}. While he expressed his support for the decision to take this stance at the time, he argued that the German media is self-censoring and generally shows too little tolerance towards anti-immigration attitudes, thereby excluding those holding such views from political discourse.

This case presents a unique case to study the effects of media content on public opinion. As I will show below, the emphasis of crime strongly increased in *Bild*'s migration coverage following Reichelt's takeover. The change of editor itself was not discussed in the media, which means any opinion changes among readers can only be the result of the changing content [see @Spirig2020]. Additionally, the timing of the editorial change is potentially exogenous, given the pressure from allegations against Diekmann. In summary, *this case is as close as possible to a field experiment in which a specific consideration of migration coverage is amplified in the coverage of one newspaper, but not others*.

@@

To measure migration framing in the news, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets **Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt* and the major German tabloid *Bild* for the period 2013-2019 (for the market reach of each outlet, see table 1 in the appendix). Following the value-expectancy model, I identify crime frames in migration coverage in a two-step process: first, I use supervised machine learning to identify content about migration. Second, I identify content about crime *within* migration coverage by applying another supervised classifier. This approach closely resembles the value-expectancy model outlined in section \@ref(framing-effects), as I first identify coverage about the *issue*, before identifying the considerations emphasized in the discussion of this issue.

To identify whether an article is about migration, I employ supervised machine learning. As migration content is rare, and sufficient training data needs to be available to train functional classifiers, articles cannot be selected randomly for annotation\footnote{If migration content made up about 3% of all articles and the sample were selected randomly, one would find around 30 migration articles per 1000 articles, which provides rather limited information about the class of interest and results in worse recall of the classifier, as the best guess in highly imbalanced data is simply the most common outcome.}. Instead, I first construct a dictionary of terms related to migration. I use dictionary extension based on German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles. Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from articles with no migration terms, 100 from the quarter with the highest share of migration terms and 100 from the remaining articles with relative frequencies of migration-related terms in between these two groups) for each newspaper for a total of 1,800 papers. Then, a coder hand-coded these articles, assessing whether their main topic is related to migration\footnote{A precise description of the classification process for migration and crime-related articles, including sampling dictionaries, instructions for coders, and preprocessing steps, can be found in appendix 1.2.}.

Using this sample, a BERT transformer model\footnote{\url{https://huggingface.co/bert-base-german-cased}} is fine-tuned on a random subset of 1,400 annotated articles (training set) with a validation set of 200 articles. After fine-tuning, the model correctly classifies 95.5% of a test set of 200 articles (F1: 0.94, recall: 0.93, precision: 0.95). This classifier is then used to annotate all 2.5 million newspaper articles. For the period from 2013 to 2019, around 90,000 (3.6%) are identified to treat the issue of migration.

To identify migration coverage containing the crime consideration and thereby associating migration with crime, I first fine tune a BERT classifier for German language in a similar fashion as above, this time with coverage about crime as the outcome of interest. Using a training set of 1400 articles, a validation set of 200 and a test set of 200 articles, the classifier reaches a very good performance with an F1 score of 85.7%. I then apply this classifer to identify the approximately 90,000 articles about migration identified by the first classifier. About 7% of all migration coverage consists of articles about some form of crime\footnote{See appendix 1.2 for more information about the classifier, training process and data.}. The share of migration content devoted to news about crime allows me to assess the prominence of the consideration of crime within migration coverage. Exemplifying the narture of the treatment, table \@ref(tab:exampleArticles) displays the headlines of the five migration articles within *Bild* which were identified to discuss crime with the highest likelihood. All articles refer to crimes of migrant groups, with two referring to violence in refugee homes, two discussing police raids regarding asylum fraud, and one discussing a police report about the sexual assaults surrounding new years eve in cologne.

@@

The left panel of figure \@ref(fig:treatment) shows the share of migration coverage devoted to crime news (solid, red line), once for Bild and once for all other newspapers (dashed, black line). As we can see, *Bild*'s attention to crime news in its migration coverage substantially increased directly following the takeover of Julian Reichelt, while it focused less on the issue preceding the editorial change\footnote{Note that this data is corrected for large changes in the overall number of articles being published by Bild. These chacnges can be traced back to a changing share of content from the German news agency dpa, which provides services to quickly distribute breaking news similar to the Associated Press. Estimates including content from dpa indicate a change in attention to crime of even larger size (6 percentage points), as can be seen in appendix 1.4.}. The trends run parallel to each other preceding the treatment. The lower attention to crime in 2015 and the increase in 2016 is in line with prior research [@Maurer2019]. The right-hand panel shows difference-in-difference estimates of the crime emphasis in migration coverage of one newspaper compared to all others, before and after the editorial change in *Bild*. One can see that *Bild* was the only newspaper which substantially changed its emphasis of the frame, increasing the share of articles devoted to crime by around 5 percentage points, while other newspapers maintained their levels of attention.

@@

The panel also contains a question on newspaper consumption, which was asked in seven waves. The question provides respondents with a list of the six major daily newspapers plus an option "another daily newspaper", and asks whether they had consumed the paper in print or read articles from their website, and if so, how many days in the past week.

@@

To provide a baseline expectation regarding the effect from experimental work, it is useful to consider the expected effect size at this point. Despite the abundance of framing effects studies, there is no common standard to assess the magnitude of framing effects. Even the correct measurement of the magnitude is a contested question, as different control groups can be compared [@Druckman2001; @Chong2007a, 109f for a discussion]. Additionally, framing effects differ based on the polarization and salience of the issue [@Lecheler2009b], repeated exposure [@Chong2007competitiveFraming], the sender [@Slothuus2010], political knowledge [@Chong2007b], as well as the reference of certain groups [@Nelson1996]. Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results lie in between 10% and 25% of the scale when comparing opposing frames pushing respondents in opposite directions\footnote{As many studies do not include a control group, this is the most comparable metric.} [@Lecheler2009b; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010]. As experimental treatments are likely designed in order to elicit strong responses, and given biases towards null effects in the production of scientific knowledge [see e.g. the recent debate regarding nudging effects: @Maier2022], reported effects likely display a selection bias towards strong treatments. The treatment can be considered rather strong here, as the crime consideration is associated with a strongly negative evaluation and the relative increase in the prevalence of this content is large \footnote{5 percentage point increase compared to pre-treatment share of 8.36 percent in Bild, a 60 percent increase.}. Given these considerations, I expect an effect of around 10% of the scale, or 0.6 on the seven-point scale\footnote{As the scale runs from one to seven, it spans six points wide.}, which represents a conservative estimate compared to reported experimental effects.

@@

Figure \@ref(fig:singleplot) visualizes the effect of the change in framing on immigration attitudes. Dashed vertical lines indicate the expected effect from the experimental literature. The dotted lines indicate the equivalence boundaries. If the 95% interval is contained within these boundaries, the hypothesis that the estimate is larger than the SESOI can be rejected. The point estimate indicates a `r round(ATT, 3)`-point change among Bild readers following treatment (*t =* `r round(t_ATT, 2)`, *p =* `r round(p_ATT, 2)`), which is around `r round(ATT*100/0.6)`% of the expected effect of 0.6. The 95% confidence interval also contains values far smaller than the SESOI of 0.15 but clearly include the vertical solid red line indicating no change. Surprisingly, the model suggests a clear null effect.

@@

As outlined above, framing theory suggests that increased exposure to a specific consideration about an issue leads to stronger association of the issue with this consideration. In the present case, this should mean that the correlation of attitudes on immigration with attitudes about crime should increase. The GLES Panel data contains a variable asking respondents whether "the state's capabilities to fight crime should be extended, even if that would entail more surveillance", asked in three waves overlapping with the migration attitude question.

Figure \@ref(fig:corplot) shows the correlation of crime- and migration attitudes in treatment (Bild-readers in pre-wave) and control group (never Bild-readers), pre- and post-treatment. I added a counterfactual, applying the change in the control group to the treatment group, for easier interpretation. As we can see, the treatment group actually saw a *smaller* increase in the correlation of crime and migration attitudes than the control group, *despite weaker pre-treatment association*. Following [@Nelson1996], table \@ref(tab:cortable) regresses immigration attitudes on attitudes towards crime and investigates whether this association is generally different between the two groups\footnote{These differences are however in the opposite direction as the (substantial) differences in the descriptive correlations outlined in the plot. I am currently not sure how to interpret this.}, changes post-treatment, and whether it changes more in the treatment group using interaction terms. I find minor differences between the groups, but no significant difference when interacted with the DiD-term - respondents do not seem to associate crime more strongly with migration following the change in migration coverage in *Bild*.

@@

MigCrimeCorPlot()

@@

@@

[explain why this is done, and why constituent terms are not interesting - only the change in association of crime attitude and dependent variable is of interest, we are not trying to explain variation in the dependent variable! (which is also why R2 doesn't matter here)]

>>>>

---
title: "Framing Effects in the Wild"
author: "Nicolai Berk"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: false
    fig_caption: yes
    includes:
      in_header: preamble.tex
# subtitle: Manuscript prepared for the 12th Annual Conference of the European Political Science Association in Prague, Czech Republic
fontsize: 12pt
geometry: margin=1.5in
abstract: "Does news framing affect public opinion? While a large body of experimental work suggests that individual attitudes can be easily altered by emphasizing different aspects of an issue, little is known about how these studies translate into the real world. I exploit a rare change in the migration framing of the major German tabloid *Bild* to study whether experimental estimates of framing effects translate into the real world. In a first step, I develop a framework for the measurement of emphasis frames in political communication using supervised machine learning. Using this framework, I show that the emphasis of crime in *Bild*'s migration coverage severely increased. Second, I employ a difference-in-differences design using panel data from over 16,000 individuals in ten waves to assess the precise impact of this shift on migration attitudes. The findings show that, despite a major change in migration framing, a clear null effect on immigration attitudes and related variables can be observed. Tracing three key assumptions underlying the translation of experimental effect estimates suggests that news framing affects attitudes only within limited windows of opportunity early in the politicization of political issues."
bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
nocite: |
  @CologneReport2016
indent: true
---

@@

knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center', eval = T, fig.pos = "!h", out.extra = "")

@@

\medskip

\noindent \textit{\textbf{Association hypothesis}: When an individual is exposed more to a specific consideration about an issue, their association of the issue with this consideration should be strengthened.}

\noindent \textit{\textbf{Evaluation hypothesis}: When an individual is exposed more to a specific positive/negative consideration about an issue, their attitude about the overall issue should become more positive/negative.}

@@

In order to test whether changing news content affected political attitudes, I exploit an editorial change in the largest German newspaper, *Bild*. As I will show, this editorial change resulted in a substantial shift in the papers' migration framing and is hence ideal to assess the effect of within-newspaper content shifts. The fielding of a large-scale panel survey in the same period allows to assess the precise impact of this change in news content on consumers' migration attitudes and related variables.

@@

In the summer of 2015, Germany became sanctuary for around 800,000 refugees who had fled war, violence, and famine in Syria and elsewhere. The German public debated how to deal with the newly arriving and for the first time since the post-war years, a radical right party was likely to win representation in the national parliament. Surprisingly, given its traditional populist style and right-wing takes on migration, the major tabloid newspaper *Bild* initially maintained a somewhat balanced coverage of refugees, which - although still portraying migrants more negatively than other outlets [@Maurer2019] - even started a campaign called "#RefugeesWelcome" to gather support for the newly arriving\footnote{See \url{https://web.archive.org/web/20160114154402/https://www.bild.de/news/topics/fluechtlingshilfe/wir-helfen-buehne-42385428.bild.html}.}. This was often connected to chief editor Kai Diekmann, who hosted a refugee family in his home [@BR2015Diekmann].

About one and a half years later, in December 2016, Axel Springer, the company owning *Bild*, announced that Diekmann will leave the company. Less than a week after, it became public that prosecutors investigate Diekmann for sexual harassment. While the company claimed that this was not the reason for Diekmann's departure, the process might have been sped up as a result of the investigations\footnote{According to a former editor of the newspaper I talked to, rumors in the company at the time support this interpretation of events.} [@Spiegel2017Diekmann]. The migration coverage in *Bild* severely changed when Diekmann left the newspaper in February 2017 and Julian Reichelt took over the position as editor-in-chief. The paper increasingly started painting a picture of refugees as criminals on the tabloid's front page [@Niggemeyer2018Bild; @DLF2018Reichelt]. Headlines like "I killed 40 people and want asylum" increasingly dominated the migration coverage of the newspaper. In a speech months before he took over the position as chief editor, Reichelt outlined his motivation for such a shift in migration coverage: "I can assure you: nothing has hurt [*Bild*] economically as much as our clear, humane, empathetic stance in the refugee crisis" \footnote{Reichelt in a speech at Deutschlandfunk's conference "Formate des Politischen 2016": \url{https://vimeo.com/190347766}}. While he expressed his support for the decision to take this stance at the time, he argued that the German media is self-censoring and generally shows too little tolerance towards anti-immigration attitudes, thereby excluding those holding such views from political discourse.

This case presents a unique opportunity to study the effects of media content on public opinion. As I will show below, the emphasis of crime strongly increased in *Bild*'s migration coverage following Reichelt's takeover. The change of editor itself was not discussed in the media, which means any opinion changes among readers can only be the result of the changing content [see @Spirig2020]. Additionally, the timing of the editorial change is potentially exogenous, given the pressure from allegations against Diekmann. In summary, *this case is as close as possible to a field experiment in which a specific consideration of migration coverage is amplified in the coverage of one newspaper, but not others*.

@@

To measure migration framing in the news, I collected 2.5 million newspaper articles from the websites of the most important German broadsheets *Frankfurter Allgemeine Zeitung (FAZ), Spiegel Online (SPON), Süddeutsche Zeitung (SZ), Die Tageszeitung (TAZ), Die Welt* and the major German tabloid *Bild* for the period 2013-2019. These outlets reach a substantial share of the German public, with *Bild* distributing over 1.7 million print copies and registering over 550 million web impressions at the time (see section 1.1 in the appendix for more information). Following the value-expectancy model, I identify crime frames in migration coverage in a two-step process: first, I use supervised machine learning to identify content about migration. Second, I identify content about crime *within* migration coverage by applying another supervised classifier. This approach closely resembles the value-expectancy model outlined in section \@ref(framing-effects), as I first identify coverage about the *issue*, before identifying the consideration emphasized in the discussion of this issue.

To identify whether an article is about migration, I employ supervised machine learning. As migration content is rare, and sufficient training data needs to be available to train functional classifiers, articles cannot be selected randomly for annotation\footnote{If migration content made up about 3 percent of all articles and the sample were selected randomly, one would find around 30 migration articles per 1000 articles, which provides rather limited information about the class of interest and results in worse recall of the classifier, as the best guess in highly imbalanced data is simply the most common outcome.}. Instead, I first construct a dictionary of terms related to migration. After constructing a seed dictionary of migration-related terms, I apply dictionary extension using German GloVe word-embeddings\footnote{Downloadable from \url{https://deepset.ai/german-word-embeddings}.} to construct a comprehensive dictionary, and apply it to the articles\footnote{The dictionary can be found in appendix XX.}. Based on the relative share of migration words in an article, I draw a stratified sample of 300 articles (100 from articles with no migration terms, 100 from the quarter with the highest share of migration terms and 100 from the remaining articles with relative frequencies of migration-related terms in between these two groups) for each newspaper for a total of 1,800 papers. Then, a coder hand-coded these articles, assessing whether their main topic is related to migration\footnote{The coder was instructed to annotate articles referring to migration or integration, which includes discussions of refugee numbers, immigrants' and naturalization rights, and general reports of migration.}.

Using this sample, a BERT transformer model\footnote{\url{https://huggingface.co/bert-base-german-cased}} is fine-tuned on a random subset of 1,400 annotated articles (training set) with a validation set of 200 articles. After fine-tuning, the model correctly classifies 95.5% of a test set of 200 articles (F1: 0.94, recall: 0.93, precision: 0.95). This classifier is then used to annotate all 2.5 million newspaper articles. For the period from 2013 to 2019, around 90,000 (3.6%) are identified to treat the issue of migration\footnote{A precise description of the classification process for migration and crime-related articles, including sampling dictionaries, instructions for coders, and preprocessing steps, can be found in appendix 1.2.}.

To identify migration coverage containing the crime consideration and thereby associating migration with crime, I first fine tune a BERT classifier for German language in a similar fashion as above, this time with coverage about crime as the outcome of interest. Using a training set of 1400 articles, a validation set of 200 and a test set of 200 articles, the classifier reaches a very good performance with an F1 score of 85.7%. I then apply this classifier to identify the approximately 90,000 articles about migration identified by the first classifier. About 7% of all migration coverage consists of articles about some form of crime. Exemplifying the nature of the coverage, table \@ref(tab:exampleArticles) displays the headlines of the five migration articles within *Bild* which were identified to discuss crime with the highest likelihood. All articles refer to crimes of migrant groups, with two referring to violence in refugee homes, two discussing police raids regarding asylum fraud, and one discussing a police report about the sexual assaults surrounding new years eve in cologne.

@@

The left panel of figure \@ref(fig:treatment) shows the share of migration coverage devoted to crime news (solid, red line), once for Bild and once for all other newspapers (dashed, black line). As we can see, *Bild*'s attention to crime news in its migration coverage substantially increased directly following the takeover of Julian Reichelt, while it focused less on the issue preceding the editorial change\footnote{Note that this data consists exclusively of original Bild content. Treatment estimates including third-party authored content are similar in size. For a more extensive discussion see appendix XX.}. The trends run parallel to each other preceding the treatment. The lower attention to crime in 2015 and the increase in 2016 is in line with prior research [@Maurer2019]. The right-hand panel shows difference-in-difference estimates of the crime emphasis in migration coverage of one newspaper compared to all others, before and after the editorial change in *Bild*. One can see that *Bild* was the only newspaper which substantially changed its emphasis of the frame, increasing the share of articles devoted to crime by around 5 percentage points, while other newspapers maintained their levels of attention.

@@

To measure exposure to *Bild* news I use a question on newspaper consumption, which was asked in seven waves. The question provides respondents with a list of the six major daily newspapers plus an option "another daily newspaper", and asks whether they had consumed the paper in print or read articles from their website, and if so, how many days in the past week. Readers are defined as *treated* if they indicate to read *Bild* in the pre-treatment wave and as *untreated* if they indicate not to read the tabloid in the pre-treatment wave, nor any subsequent wave\footnote{See appendix XX for descriptives of all mentioned variables.}.

In order to assess the effect on the association of immigration and crime, I also measure attitudes about crime using an item asking whether the governments' capabilities to fight crime should be extended\footnote{Precise question wording: "State powers to fight crime should be expanded, even if this means more surveillance of citizens."} on a 5-point Likert-scale. I also use additional dependent variables assessing attitudes about the need for immigrants to integrate into German culture (7-point scale), mentioning immigration as the most important problem (binary indicator), and a thermometer score for the radical-right *AfD* (10 point scale).

@@

To provide a baseline expectation regarding the effect from experimental work, it is useful to consider the expected effect size at this point. Despite the abundance of framing effects studies, there is no common standard to assess the magnitude of framing effects. Even the correct measurement of the magnitude is a contested question, as different control groups can be compared [@Druckman2001; @Chong2007a, 109f for a discussion]. Additionally, framing effects differ based on the polarization and salience of the issue [@Lecheler2009b], repeated exposure [@Chong2007competitiveFraming], the sender [@Slothuus2010], political knowledge [@Chong2007b], as well as the reference of certain groups [@Nelson1996]. Generally, reported effect size around 30% of the scale are not uncommon [@Slothuus2010], sometimes even over 40% [@Chong2007a, 104], but most results lie in between 10% and 25% of the scale when comparing opposing frames pushing respondents in opposite directions\footnote{As many studies do not include a control group, this is the most comparable metric.} [@Lecheler2009b; @Nelson1997Psychology; @Nelson1997Rally; @Slothuus2008; @Slothuus2010]. [add reference to GSS running welfare panel with welfare vs assistance to the poor form \url{https://www.youtube.com/watch?v=a_CmfRjZ_oY}. Problem with this: much better data to show your argument, kinda opposite result - look into this though, maybe after finishing the paper!]

As experimental treatments are likely designed in order to elicit strong responses, and given biases towards null effects in the production of scientific knowledge [see e.g. the recent debate regarding nudging effects: @Maier2022], reported effects likely display a selection bias towards strong treatments. The treatment can be considered rather strong here, as the crime consideration is associated with a strongly negative evaluation and the relative increase in the prevalence of this content is large \footnote{5 percentage point increase compared to pre-treatment share of 8.36 percent in Bild, a 60 percent increase.}. Given these considerations, I expect an effect of around 10% of the scale, or 0.6 on the seven-point scale\footnote{As the scale runs from one to seven, it spans six points wide.}, which represents a conservative estimate compared to reported experimental effects.

@@

[simplify all of these sections, follow economist papers from course]

According to the expectancy-value model (see section \@ref{framing-effects}), the most direct implication of increased exposure to crime frames in migration coverage should be a more conservative assessment of immigration. Figure \@ref(fig:singleplot) visualizes the effect of the change in framing on immigration attitudes, with higher values indicating that *Bild* readers change their attitudes in a more restrictive direction, compared to the control group. Dashed vertical lines indicate the expected effect from the experimental literature. The dotted lines indicate the equivalence boundaries. Surprisingly, the model suggests a clear null effect. This effect is not significantly different from zero, but significantly smaller than the above-defined minimal effect of 0.15 on the seven-point Likert scale. The point estimate indicates a `r round(ATT, 3)`-point change among *Bild* readers following treatment (*t =* `r round(t_ATT, 2)`, *p =* `r round(p_ATT, 2)`). This represents only a fraction (`r round(ATT/0.6, 3)*100`%) of the already conservative experimental estimate of 0.6.

@@

Framing theory suggests that increased exposure to a specific consideration about an issue also leads to stronger association of the issue with this consideration. In the present case, this should mean that the correlation of attitudes on immigration with attitudes about crime should increase. The GLES Panel data contains a variable asking respondents whether "the state's capabilities to fight crime should be extended, even if that would entail more surveillance", asked in three waves overlapping with the migration attitude question.

```{r corests}

bs <- MigCrimeCorPlotBS(return_ests = T)

deltas_3 <- 
  (bs[["mig_crime_cor"]][bs$treat & bs$wave == 3] - 
    bs[["mig_crime_cor"]][bs$treat & bs$wave == 1]) -
  (bs[["mig_crime_cor"]][!bs$treat & bs$wave == 3] - 
    bs[["mig_crime_cor"]][!bs$treat & bs$wave == 1])

deltas_13 <- 
  (bs[["mig_crime_cor"]][bs$treat & bs$wave == 13] - 
    bs[["mig_crime_cor"]][bs$treat & bs$wave == 1]) -
  (bs[["mig_crime_cor"]][!bs$treat & bs$wave == 13] - 
    bs[["mig_crime_cor"]][!bs$treat & bs$wave == 1])

Figure \@ref(fig:corplot) shows the bootstrapped correlations of crime- and migration attitudes in treatment (Bild-readers in pre-wave) and control group (never Bild-readers), pre- and post-treatment. The lines indicate the mean estimate, while the whiskers indicate the upper and lower 95%-confidence interval, as defined by the 2.5% and 97.5% percentiles of the distribution of estimates of the correlation. I added a counterfactual, applying the changes in the control group to the treatment group, for easier interpretation. Surprisingly, the association of crime and immigration attitudes is initially weaker among *Bild* readers. Nevertheless, the treatment group actually saw a *smaller* increase in the correlation of crime and migration attitudes in the first post-treatment wave than the control group. The difference-in-differences in correlations of `r round(mean(deltas_3), 3)` is substantively rather small (`r abs(mean(deltas_3)/mean(bs[["mig_crime_cor"]][!bs$treat & bs$wave == 1])) %>% round(3)` of the average pre-treatment control group correlation) and not significantly different from zero with a bootstrapped 95% confidence interval of [`r quantile(deltas_3, 0.025)[[1]] %>% round(3)`, `r quantile(deltas_3, 0.975)[[1]] %>% round(3)`]. In the last wave, the association decreases less than in the control group but the difference-in-differences does not reach conventional levels of significance compared to the pre-treatment wave (`r round(mean(deltas_13), 3)`, [`r quantile(deltas_13, 0.025)[[1]] %>% round(3)`, `r quantile(deltas_13, 0.975)[[1]] %>% round(3)`]).

@@

MigCrimeCorPlotBS()

@@

Following [@Nelson1996], table \@ref(tab:cortable) also regresses immigration attitudes on attitudes towards crime and investigates whether this association changes as a result of the change in coverage (note that all constituent terms are included but only those regarding the association of crime and immigration attitudes reported). Similar to the differences between the groups, I find a weaker association among readers of the tabloid, but no significant or substantively large difference post-treatment or when interacted with the DiD-term. Respondents do not seem to associate crime more strongly with migration following the change in migration coverage in *Bild*.

@@
